Supermassive black holes and host bulges affairs -- \\ II. The red and the blue sequences in the mass -- mass diagram.

### 2015-04-24 papers/MbhMsph/mm.tex
friiiiiiday

\title{M-M paper, morphological dependence, red sequence }

@@

\begin{abstract}
We present the latest scaling relations between black hole mass, $M_{\rm BH}$, 
and spheroid luminosity, $L_{\rm sph}$, spheroid stellar mass, $M_{\rm *,sph}$, and galaxy luminosity, $L_{\rm gal}$,
built upon an unprecedented high-quality data set (provided here in a ready-to-use table).
Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
Spheroid luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
which is minimally affected by dust and star formation. 
These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
Previous studies used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to investigate the poorly studied low-mass end of the correlations.
We provide updated linear regressions 
(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
The bulges of early-type (E/S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$, 
as expected from a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon = 0.43 \pm 0.06$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
indicating that gas-rich processes feed the black hole three times more efficiently than the host bulge. 
Disproving some previous claims, we also conclude that: 1) S\'ersic and core-S\'ersic galaxies do not define two distinct sequences; 
2) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
3) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well, in terms of intrinsic scatter, with $M_{\rm BH}$ only for early-type galaxies.

@@

\section{Data}
\label{sec:data}
Our galaxy sample (see Table \ref{tab:sample}) 
consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
(GS13, \citealt{rusli2013bhmassesDM}) at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Bulge magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
to confirm the presence of rotationally supported components in most early-type galaxies, 
and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
discuss how we estimated the uncertainties on the bulge parameters, 
and illustrate the individual 66 galaxy decompositions. \\
Bulge luminosities\footnote{Absolute luminosities were calculated 
assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
were first converted into stellar masses using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
We then explored a more sophisticated way to compute mass-to-light ratios, 
using the color-$\Gamma_{3.6}$ relation published by 
\citeauthor{meidt2014} (\citeyear{meidt2014}, their equation 4), 
which allows one to estimate $\Gamma_{3.6}$ of a galaxy from its $[3.6] - [4.5]$ color. 
Individual $[3.6] - [4.5]$ colors\footnote{These are integrated $[3.6] - [4.5]$ colors, measured in a circular aperture 
within one galaxy's effective radius.} were taken from 
\citeauthor{peletier2012} (\citeyear{peletier2012}, column 8 of their Table 1) 
when available for our galaxies, 
or were estimated from the bulge stellar velocity dispersion, $\sigma$, 
using the color-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
We found that the range in $[3.6] - [4.5]$ color is small ($0.06\rm~mag$), 
and thus the range in $\Gamma_{3.6}$ is also small ($0.04$).
After checking that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ color, 
does not significantly affect the results of our analysis, 
we decided to use individual, color-dependent mass-to-light ratios. \\
The S\'ersic/core-S\'ersic classification presented in this work 
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by GS13.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\
For each galaxy, the total luminosity (or galaxy luminosity, $L_{\rm gal}$) is the sum of the luminosities of all its sub-components. 
Due to the complexity of their modelling, 
four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 
which are given here as lower limits.

@@

\begin{figure}[h]
\begin{center}
%\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_galsymb_agn.pdf}
\caption{Black hole mass against spheroid stellar mass. 
The galaxies from our sample are shown with large symbols (red = E, orange = E/S0 and S0, blue = S0/Sp and Sp, black = merger).
The 139 small blue dots represent the low-mass AGN sample from \cite{jiang2011a}. 
The blue crossed circles denote 35 additional galaxies (see \citealt{grahamscott2015}, their Table 2), 
some of which might have had their bulge stellar masses overestimated.
The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. }
\label{fig:mbhmasssph}
\end{center}
\end{figure}

@@

\section{Analysis}
\label{sec:anal}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$, $M_{\rm BH} - M_{\rm *,sph}$ and $M_{\rm BH} - L_{\rm gal}$ diagrams 
using the BCES code from \cite{akritasbershady1996} 
and also the FITEXY routine \citep{press1992} 
modified by \cite{tremaine2002} to account for the intrinsic vertical scatter, $\epsilon$. 
Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
can give biased results (wrong slope) when the scatter is comparable to the range of the data},
we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
In Table \ref{tab:lreg} we report the BCES and modified FITEXY linear regressions, both symmetrical and non-symmetrical, 
for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas non-symmetrical Ordinary Least Squares $(Y|X)$ regressions -- 
since they minimize the scatter in the vertical direction -- 
can be used to predict black hole masses.

@@

\subsection{Black hole mass -- spheroid luminosity}
We show the $M_{\rm BH} - L_{\rm sph}$ diagram in Figure \ref{fig:mbhmagsph}. \\
S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
in disagreement with the findings of GS13. 
The slope that we obtained for core-S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.2 \pm 0.2}$) 
is consistent with the slope reported by GS13 in the $K_s$-band ($M_{\rm BH} \propto L_{\rm sph}^{1.1 \pm 0.2}$). 
Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.5 \pm 0.2}$) 
is significantly shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.7 \pm 0.5}$). 
Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{which galaxies?} from the classification used here, 
the main cause of such inconsistency is that the bulge-to-total ratios obtained from our galaxy decompositions 
are different from those assumed by GS13 to convert galaxy luminosities into bulge luminosities.
Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($MAG_{\rm sph} \gtrsim -22 \rm~mag$) 
are smaller than those used by GS13. 
The host galaxies of such bulges are late-type, spiral galaxies, 
which typically present a complex morphology (bars, double bars, embedded disks, nuclear components, etc).
Our sophisticated galaxy models account for the extra components, 
while the bulge-to-total ratios of GS13 were derived from simple bulge/disk decompositions 
which overestimated the bulge luminosity.
This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter.
On the other side, our bulge-to-total ratios for high-luminosity S\'ersic spheroids ($MAG_{\rm sph} \lesssim -24 \rm~mag$) 
are on average larger than those adopted by GS13.
In this case, the host systems are early-type elliptical/lenticular galaxies that feature intermediate-scale disks\footnote{explain}.
Past bulge/disk decompositions failed to correctly identify the extent of such disks and treated them as large-scale disks, 
thus underestimating the bulge luminosity.
The magnitudes that we obtained for such spheroids are on average $\sim$$1\rm~mag$ brighter. \\
We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 
which is expected for consistency with other scaling relations 
(a single power-law $M_{\rm BH} - \sigma$ correlation and a double power-law $L_{\rm sph} - \sigma$ correlation) -- 
cannot be attributed to the division between the two populations of S\'ersic and core-S\'ersic spheroids.
We now test a new hypothesis, that is to say the change in slope is to be ascribed to the different formation mechanisms of early- and late-type galaxies. 
If this hypothesis is correct, 
the spheroids of early-type (elliptical and lenticular) galaxies will follow $M_{\rm BH} \propto L_{\rm sph}^{\sim 1}$, 
whereas the spheroids of late-type (spiral) galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.
First, we checked that the slopes of the bulges of elliptical and lenticular galaxies, separately, are consistent with each other, 
and thus, together, they define a single \emph{red sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
We then fit the bulges of early- and late-type galaxies with two separate log-linear regressions, 
and obtained $M_{\rm BH} \propto L_{\rm sph}^{1 \pm 0.1}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.75 \pm 0.75}$ respectively, 
in excellent agreement with the theoretical expectations of our hypothesis.
{\bf vertical scatter along the early type sequence is constant?
if 2 overmassive bhs removed, what happens?}

{\bf coming now to figure 1: if I look at the blue points it is difficult to believe that they define a linear relation, 
their magnitude range is too small and it could just be that at low galaxy luminosities the scatter of the MBH-L relation increases. 
This is what most models predict. Do the galaxies below the correlation have some special property? 
Could it just be that spiral bulges simple do not follow a tight relation with BH mass?

Giulia, I think you already plan to do this, but can you include the error bars in all places where a relation is presented, so that readers know if there is a relation or not.
Remember also Ewan's remark about the unsuitability of the Pearson and Spearman correlation coefficients because they do not take into account the error bars on our data - 
so don't include those simple coefficients.  Actually, it would be worth pointing out to readers that a visual inspection of the plotted data requires 
the viewer to take into account the error bars when judging-by-eye the strength of a correlation. 
Maybe then mention in the following sentence that this is why the correlation coefficients are not applicable here. }

In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).}, 
$n_{\rm sph}$, in the $M_{\rm BH} - L_{\rm sph}$ diagram.
Our aim is to check whether bulges with $n_{\rm sph}<2$, claimed by some to be pseudobulges (e.g.~ cite), 
are offset to lower black hole masses from the correlation defined by (classical) bulges with $n_{\rm sph}>2$, 
as reported by \cite{sani2011} {\bf who else?}. 
To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
and we compute the vertical offset of all bulges from the regression. 
In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.

{\bf As you probably know, and as explained in many of my papers (e.g. http://arxiv.org/abs/1501.02937 ; http://arxiv.org/abs/1108.0997 ; http://arxiv.org/abs/1311.7207 ), 
pseudobulges are notoriously hard to identify.  It would be a mistake to have a column labelled "pseudobulge".   
However a galaxy classification column, indicating the presence of a bar, is good to include.  
While we do not wish to publish the Sersic indices here (that will be kept for a different paper), 
we could have a column indicating if n is above or below 2 - given that some people mistakingly think that they can use this as a dividing point. 
Giulia, can you also include a nearby reference to Graham (2013, http://arxiv.org/abs/1108.0997) so that people can read and understand why $n < 2$ 
does not necessarily equate to a pseudobulge. }

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis. 
\cite{lasker2014anal}

Contrary to a previous claim, the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.

compare scatter mbh-msph and mbh-mgal for early types
intrinsic scatter of early type gals in m-mbul is slightly more than in m-mgal, but this might just depend 
on the ability of measuring the bulge luminosity, which is model dependent, the gal lum is not.
only for early type galaxies one can use the tot luminosity as bh mass indicator

errors on gal mag??????????????? 0.2 constant

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}, 
where we include our sample of 66 galaxies, 
plus the 35 + 139 low-mass AGNs taken from the compilation of \cite{grahamscott2015}.

addition of agns
relations
agns consistent w spirals, but analysis deferred to other paper
cubic growth

>>>>

\title{Supermassive black holes and host bulges affairs -- \\ II. The red and the blue sequences in the mass -- mass diagram.}

@@

\begin{abstract}
We present the latest scaling relations between black hole mass, $M_{\rm BH}$, 
and spheroid luminosity, $L_{\rm sph}$, spheroid stellar mass, $M_{\rm *,sph}$, and galaxy luminosity, $L_{\rm gal}$,
built upon an unprecedented high-quality data set (provided here in a ready-to-use table).
Our sample, the largest ever used, counts 66 local galaxies with a dynamical measurement of $M_{\rm BH}$.
Luminosities come from high signal-to-noise $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
which is minimally affected by dust and star formation. 
These luminosities were derived from our state-of-the-art multicomponent galaxy decompositions, 
that take into account bulges, disks, bars, spiral arms, rings, haloes, extended or unresolved nuclear sources and partially depleted cores, 
and that -- for the first time -- were checked to be consistent with the galaxy kinematics. 
Previous studies used galaxy samples that were overwhelmingly dominated by high-mass, early-type objects.
Instead, our sample includes 17 spiral galaxies, half of which have $M_{\rm BH} < 10^7\rm~M_\odot$, 
and allows us to investigate the poorly studied low-mass end of the correlations.
We provide updated linear regressions 
(symmetrical, to be compared with theoretical expectations, and non-symmetrical, to be used to predict black hole masses) 
for S\'ersic/core-S\'ersic galaxies and for different morphological types (E/S0, Sp). 
The bulges of early-type (E/S0) galaxies follow $M_{\rm BH} \propto M_{\rm *,sph}^{1.0 \pm 0.1}$, 
as expected from a dry-merging formation scenario,
and define a tight \emph{red sequence} with intrinsic scatter $\epsilon = 0.43 \pm 0.06\rm~dex$.
On the other hand, the bulges of late-type (Sp) galaxies define a much steeper \emph{blue sequence}, 
with $M_{\rm BH} \propto M_{\rm *,sph}^{3.0 \pm 1.3}$, 
indicating that gas-rich processes feed the black hole three times more efficiently than the host bulge. 
Disproving some previous claims, we also conclude that: 1) S\'ersic and core-S\'ersic galaxies do not define two distinct sequences; 
2) bulges with S\'ersic index $n_{\rm sph}<2$, argued by some to be pseudo-bulges, 
are not offset to lower $M_{\rm BH}$ from the correlation defined by bulges with $n_{\rm sph}>2$; 
3) $L_{\rm sph}$ and $L_{\rm gal}$ correlate equally well with $M_{\rm BH}$, in terms of intrinsic scatter, only for early-type galaxies.

@@

\section{Data}
\label{sec:data}
Our galaxy sample (see Table \ref{tab:sample}) 
consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
(by GS13 or \citealt{rusli2013bhmassesDM}) at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Bulge magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
to confirm the presence of rotationally supported components in most early-type galaxies, 
and to identify their extent 
(intermediate-scale disks, that are fully embedded in the bulge, 
or large-scale disks, that encase the bulge and dominate the light at large radii). 
\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
discuss how we estimated the uncertainties\footnote{By comparing, for our galaxies, the measurements of the bulge magnitude 
obtained by different authors with those obtained by us, we estimated the uncertainties on the bulge magnitudes 
with a method that takes into account systematic errors. 
Systematic errors include incorrect sky subtraction, inaccurate masking of contaminating sources, imprecise description of the PSF, 
erroneous choice of model components (for example, when failing to identify a galaxy subcomponent and thus omitting it in the model, 
or when describing a galaxy sub-component with an inadequate function), 
the radial extent of the surface brightness profile and its sampling. 
These factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters. 
In fact, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well spatially resolved -- galaxies, 
errors are dominated by systematics rather than Poisson noise.} 
on the bulge magnitudes, and illustrate the individual 66 galaxy decompositions. \\
Bulge luminosities\footnote{Absolute luminosities were calculated 
assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
were first converted into stellar masses using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
We then explored a more sophisticated way to compute mass-to-light ratios, 
using the color-$\Gamma_{3.6}$ relation published by 
\citeauthor{meidt2014} (\citeyear{meidt2014}, their equation 4), 
which allows one to estimate $\Gamma_{3.6}$ of a galaxy from its $[3.6] - [4.5]$ color. 
Individual $[3.6] - [4.5]$ colors\footnote{These are integrated $[3.6] - [4.5]$ colors, measured in a circular aperture 
within one galaxy's effective radius.} were taken from 
\citeauthor{peletier2012} (\citeyear{peletier2012}, column 8 of their Table 1) 
when available for our galaxies, 
or were estimated from the bulge stellar velocity dispersion, $\sigma$, 
using the color-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
We found that the range in $[3.6] - [4.5]$ color is small ($0.06\rm~mag$), 
and thus the range in $\Gamma_{3.6}$ is also small ($0.04$).
After checking that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ color, 
does not significantly affect the results of our analysis, 
we decided to use individual, color-dependent mass-to-light ratios. \\
The S\'ersic/core-S\'ersic classification presented in this work 
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by GS13.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\
For each galaxy, the total luminosity (or galaxy luminosity, $L_{\rm gal}$) is the sum of the luminosities of all its sub-components. 
Due to the complexity of their modelling, 
four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 
which are given here as lower limits. 
Following GS13, we assumed a constant uncertainty of $0.25\rm~mag$ for all galaxy magnitudes.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph.pdf}
\caption{Black hole mass against spheroid stellar mass. 
Symbols are coded according to the galaxy morphological type (red = E, orange = E/S0 and S0, blue = S0/Sp and Sp, black = merger).
The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. }
\label{fig:mbhmasssph}
\end{center}
\end{figure}

@@

\section{Analysis}
\label{sec:anal}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$, $M_{\rm BH} - M_{\rm *,sph}$ and $M_{\rm BH} - L_{\rm gal}$ diagrams 
using the BCES code from \cite{akritasbershady1996}. 
We also repeated the analysis with the FITEXY routine \citep{press1992}, modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}. 
Although all these three linear regression routines account for the intrinsic scatter, 
only the last two allow to quantify it.
%Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
%can give biased results (wrong slope) when the scatter is comparable to the range of the data},
%we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
In Table \ref{tab:lreg}, we report the BCES, modified FITEXY and {\tt linmix\_err} linear regressions, both symmetrical and non-symmetrical, 
for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas non-symmetrical Ordinary Least Squares $(Y|X)$ regressions -- 
since they minimize the scatter in the vertical direction -- 
can be used to predict black hole masses.

@@

\subsection{Black hole mass -- spheroid luminosity}
We show the $M_{\rm BH} - L_{\rm sph}$ diagram in Figure \ref{fig:mbhmagsph}. \\
S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
in disagreement with the findings of GS13. 
The slope that we obtained for core-S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.2 \pm 0.2}$) 
is consistent with the slope reported by GS13 in the $K_s$-band ($M_{\rm BH} \propto L_{\rm sph}^{1.1 \pm 0.2}$). 
Instead, the slope that we determined for S\'ersic spheroids ($M_{\rm BH} \propto L_{\rm sph}^{1.5 \pm 0.2}$) 
is significantly shallower than that found by GS13 ($M_{\rm BH} \propto L_{\rm sph}^{2.7 \pm 0.5}$). 
Although the S\'ersic/core-S\'ersic classification used by GS13 slightly differs\footnote{which galaxies?} from the classification used here, 
the main cause of such inconsistency is that the bulge-to-total ratios obtained from our galaxy decompositions 
are different from those assumed by GS13 to convert galaxy luminosities into bulge luminosities.
Our bulge-to-total ratios for low-luminosity S\'ersic spheroids ($MAG_{\rm sph} \gtrsim -22 \rm~mag$) 
are smaller than those used by GS13. 
The host galaxies of such bulges are late-type, spiral galaxies, 
which typically present a complex morphology (bars, double bars, embedded disks, nuclear components, etc).
Our sophisticated galaxy models account for the extra components, 
while the bulge-to-total ratios of GS13 were derived from simple bulge/disk decompositions 
which overestimated the bulge luminosity.
This results in our bulge magnitudes being on average $\sim$$1\rm~mag$ fainter.
On the other side, our bulge-to-total ratios for high-luminosity S\'ersic spheroids ($MAG_{\rm sph} \lesssim -24 \rm~mag$) 
are on average larger than those adopted by GS13.
In this case, the host systems are early-type elliptical/lenticular galaxies that feature intermediate-scale disks\footnote{explain}.
Past bulge/disk decompositions failed to correctly identify the extent of such disks and treated them as large-scale disks, 
thus underestimating the bulge luminosity.
The magnitudes that we obtained for such spheroids are on average $\sim$$1\rm~mag$ brighter. \\
We have seen that the change in slope of the $M_{\rm BH} - L_{\rm sph}$ correlation -- 
which is expected for consistency with other scaling relations 
(a single power-law $M_{\rm BH} - \sigma$ correlation and a double power-law $L_{\rm sph} - \sigma$ correlation) -- 
cannot be attributed to the division between the two populations of S\'ersic and core-S\'ersic spheroids.
We now test a new hypothesis, that is to say the change in slope is to be ascribed to the different formation mechanisms of early- and late-type galaxies. 
If this hypothesis is correct, 
the spheroids of early-type (elliptical and lenticular) galaxies will follow $M_{\rm BH} \propto L_{\rm sph}^{\sim 1}$, 
whereas the spheroids of late-type (spiral) galaxies will have $M_{\rm BH} \propto L_{\rm sph}^{\sim 2.5}$.
First, we checked that elliptical and lenticular galaxies, taken separately, have slopes consistent with each other, 
and thus, taken together, they define a single \emph{red sequence} in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
We then fit the bulges of early- and late-type galaxies with two separate log-linear regressions, 
and obtained $M_{\rm BH} \propto L_{\rm sph}^{1 \pm 0.1}$ and $M_{\rm BH} \propto L_{\rm sph}^{2.75 \pm 0.75}$ respectively, 
in excellent agreement with the theoretical expectations of our hypothesis.
%{\bf vertical scatter along the early type sequence is constant? if 2 overmassive bhs removed, what happens?}
{\bf AL, can you pls write this: 
Remember also Ewan's remark about the unsuitability of the Pearson and Spearman correlation coefficients because 
they do not take into account the error bars on our data - 
so don't include those simple coefficients.  
Actually, it would be worth pointing out to readers that a visual inspection of the plotted data requires 
the viewer to take into account the error bars when judging-by-eye the strength of a correlation. 
Maybe then mention in the following sentence that this is why the correlation coefficients are not applicable here. }

\subsection{Pseudo- versus classical bulges}
Current views distinguish between classical bulges, which are considered to be spheroidal, pressure-supported systems, 
formed through violent processes, such as hierarchical clustering via minor mergers, 
and pseudo-bulges, thought to be disk-like, rotation-supported systems, 
built from secular evolution processes, such as instabilities of their surrounding disk or bar. 
Pseudo-bulges are notoriously hard to identify \citep{graham2013review,graham2014review,graham2015pseudo,graham2015review}.
For example, mergers can create bulges that rotate (e.g.~\citealt{bekki2010,keselmannusser2012}), 
and bars can spin-up classical bulges (e.g.~\citealt{saha2012}), 
thus rotation is not a definitive signature of a pseudobulge. 
Furthermore, many galaxies host both a pseudo- and a classical bulge (e.g.~\citealt{erwin2003,erwin2015,athanassoula2005,Gadotti2009,
macarthur2009,dosanjosdasilva2013,seidel2015}). 
In the recent literature, pseudo- and classical bulges have been frequently told apart by means of a divide at a 
S\'ersic index of $n_{\rm sph}=2$ (e.g.~\citealt{fisherdrory2010}), 
although, from a selection of hundreds of disc galaxies imaged in the $K$-band, 
\cite{grahamworley2008} observed no such bimodality in the bulge S\'ersic indices. 
While pseudo-bulges are expected to have exponential-like surface brightness profiles ($n_{\rm sph} \simeq 1$), 
being disky components that formed from their surrounding exponential disks 
(e.g.~\citealt{bardeen1975,hohl1975,combessanders1981,combes1990,pfennigerfriedli1991}), 
it has been shown that mergers can create bulges with $n_{\rm sph}<2$
(e.g.~\citealt{elichemoral2011,scannapieco2011,querejeta2015}), 
just as low-luminosity elliptical galaxies (not built from the secular evolution of a disk)
are well known to have $n_{\rm sph}<2$ and even $n_{\rm sph}<1$ (e.g.~\citealt{davies1988,youngcurrie1994}). \\
\cite{sani2011} reported that pseudo-bulges -- which they labelled as such according to the $n_{\rm sph}<2$ criterion -- 
with low black hole masses ($M_{\rm BH} < 10^7\rm~M_\odot$) are significantly displaced from the correlation 
traced by classical bulges. 
In Figure \ref{fig:pseudob}, we show the distribution of spheroid S\'ersic indices\footnote{The spheroid S\'ersic indices 
are taken from our one-dimensional fits of the galaxy major-axis surface brightness profiles (\emph{Paper I}).} 
in the $M_{\rm BH} - L_{\rm sph}$ diagram.
Our aim is to check whether $n_{\rm sph}<2$ bulges 
are offset to lower black hole masses from the correlation defined by $n_{\rm sph}>2$ bulges. 
To do this, we fit a symmetrical linear regression to the bulges that have $n_{\rm sph}>2$ 
and we compute the vertical offset of all bulges from the regression. 
In the inset of Figure \ref{fig:pseudob}, we plot the vertical offset against $n_{\rm sph}$. 
From a visual inspection, bulges with $n_{\rm sph}<2$ do not appear to be offset from the correlation traced by bulges with $n_{\rm sph}>2$.

\subsection{Black hole mass -- galaxy luminosity}
Figure \ref{fig:mbhmaggal} illustrates the $M_{\rm BH} - L_{\rm gal}$ diagram.
Four spiral galaxies had their total luminosities underestimated (see Section \ref{sec:data}) 
and thus are not included in the linear regression analysis. 
Upon analyzing a sample of 35 galaxies, among which only four were classified as spiral galaxies, 
\cite{lasker2014anal} claimed that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations, 
which they fit with a single power-law, have consistent intrinsic scatter.
Here, instead, thanks to our double-sized galaxy sample that includes 17 spiral galaxies, 
we show that the claim made by \cite{lasker2014anal} is valid only for early-type galaxies. 
The $M_{\rm BH} - L_{\rm sph}$ correlation for all galaxies, irrespective of their morphological type, 
has intrinsic scatter $\epsilon_{(Y|X)} = 0.51 \pm 0.06\rm~dex$ (direct linear regression) 
and $\epsilon_{(X|Y)} = 0.60 \pm 0.09\rm~dex$ (inverse linear regression), 
whereas the $M_{\rm BH} - L_{\rm gal}$ correlation for all galaxies has $\epsilon_{(Y|X)} = 0.63 \pm 0.07\rm~dex$ 
and $\epsilon_{(X|Y)} = 0.91 \pm 0.17\rm~dex$.
When considering only early-type galaxies, 
we find that the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ relations have the same level of intrinsic scatter 
($\epsilon_{(Y|X)} = 0.41 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.51 \pm 0.10\rm~dex$ 
against $\epsilon_{(Y|X)} = 0.43 \pm 0.06\rm~dex$ and $\epsilon_{(X|Y)} = 0.53 \pm 0.10\rm~dex$).
{\bf We point out here that this result does not strongly depend on the value that we assumed for the uncertainty of galaxy magnitudes (0.25). 
In fact, we tested different values and found that we need $error >= 0.7 mag$ to say that gal lum has smaller intrinsic scatter.

From the observer's perspective, measuring galaxy luminosities is obviously easier and faster 
than performing galaxy decompositions to obtain bulge luminosities. 
This, combined with the results from our analysis, suggests that one should prefer the galaxy luminosity over the bulge luminosity 
to predict black hole masses in a sample of elliptical and lenticular galaxies only.

\subsection{Black hole mass -- spheroid stellar mass}
Finally, we present the $M_{\rm BH} - M_{\rm *,sph}$ diagram in Figure \ref{fig:mbhmasssph}.

relations
agns consistent w spirals, but analysis deferred to other paper
cubic growth
